The sound of teaching music: Expert pianists' performance modulations for novices

### 2022-07-08 paper/manuscript.Rmd
add variability plots / correct significance *** on kv-diff plots
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

vel_diff_dyn_1 <- ggpaired(vel_diff_dyn_plot, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "subcomponent", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "Difference", title = "KV-Diff: Exp 1") +
  ylim(-40, 60) +
  stat_compare_means(label = "p.signif", hide.ns = TRUE, size = 10, label.x = 1.4, label.y = 45, method = "t.test", paired = TRUE) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

@@

```{r plot-ioi-2, out.width = "100%", fig.cap = "\\label{fig:ioi-2}Experiment 2: Normalised IOIs when playing the piece with either articulation (left) or dynamics (right). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box. Significance levels: * \\textit{p} < .05, ** \\textit{p} < .01, *** \\textit{p} < .001"}
img_ioi_2 <- image_append(c(img_ioi_art_2, img_ioi_dyn_2))
img_ioi_2 <- image_scale(img_ioi_2, "2200")
image_write(img_ioi_2, path = here("paper/figure", "Fig6.tiff"), format = "tiff")
img_ioi_2
```

@@

@@

>>>>

vel_diff_dyn_1 <- ggpaired(vel_diff_dyn_plot, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "subcomponent", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "Difference", title = "KV-Diff: Exp 1") +
  ylim(-40, 60) +
  stat_compare_means(label = "p.signif", hide.ns = TRUE, size = 10, label.x = 1.4, label.y = 45, method = "t.test", paired = TRUE, symnum.args = list(cutpoints = c(0, 0.0001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) + # adjust significance level according to the actual stats
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

@@

```{r plot-ioi-2, out.width = "100%", fig.cap = "\\label{fig:ioi-2}Experiment 2: Normalised IOIs when playing the piece with either articulation (left) or dynamics (right). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box. Significance levels: * \\textit{p} < .05, ** \\textit{p} < .01, *** \\textit{p} < .001"}
# combine
img_ioi_2 <- image_append(c(img_ioi_art_2, img_ioi_dyn_2))
img_ioi_2 <- image_scale(img_ioi_2, "2200")
image_write(img_ioi_2, path = here("paper/figure", "Fig6.tiff"), format = "tiff")
img_ioi_2
```

@@

```{r, echo = FALSE}
ioi_cv_plot <- data.table(subject = ioi_cv_subject[Condition == "teaching"]$SubNr, teaching = ioi_cv_subject[Condition == "teaching"]$MeanCV, performing = ioi_cv_subject[Condition == "performing"]$MeanCV, skill = ioi_cv_subject[Condition == "teaching"]$Skill)

ioi_cv_1 <- ggpaired(ioi_cv_plot, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "skill", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "CVs", title = "CVs: Exp 1") +
  ylim(0.02, 0.20) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

# save plots
ggsave(here("paper/image", "ioi_cv_1.png"), plot = ioi_cv_1, dpi = 300, width = 7, height = 5)
img_ioi_cv_1 <- image_read(here("paper/image", "ioi_cv_1.png"), density = 300)
```

@@

```{r, echo = FALSE}
ioi_cv_plot <- data.table(subject = ioi_cv_subject[Condition == "teaching"]$SubNr, teaching = ioi_cv_subject[Condition == "teaching"]$MeanCV, performing = ioi_cv_subject[Condition == "performing"]$MeanCV, skill = ioi_cv_subject[Condition == "teaching"]$Skill)

ioi_cv_2 <- ggpaired(ioi_cv_plot, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "skill", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "CVs", title = "CVs: Exp 2") +
  ylim(0.02, 0.20) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

# save plots
ggsave(here("paper/image", "ioi_cv_2.png"), plot = ioi_cv_2, dpi = 300, width = 7, height = 5)
img_ioi_cv_2 <- image_read(here("paper/image", "ioi_cv_2.png"), density = 300)
```

```{r plot-cv-1, out.width = "100%", fig.cap = "\\label{fig:vel-2}Experiment 1, 2: CVs when playing the piece with either articulation or dynamics (left: Experiment 1, right: Experiment 2). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box. Significance levels: * \\textit{p} < .05, ** \\textit{p} < .01, *** \\textit{p} < .001"}
img_ioi_cv <- image_append(c(img_ioi_cv_1, img_ioi_cv_2))
img_ioi_cv <- image_scale(img_ioi_cv, "2200")
image_write(img_ioi_cv, path = here("paper/figure", "Fig10.tiff"), format = "tiff")
img_ioi_cv
```
